### 2021-03-06 paper.Rmd
paragraph on bases notation

$d$-dimensional projection in $p$-dimensional space

Data: $X_{n \times p}$, 
Basis: $A_{p \times d}$, commonly 1d or 2d projection, orthonormality, more displays in the next section - can display a matrix A, Link to geometry properties.
projection: $Y = X \cdot A$

>>>>

Some notations are defined for describing $d$-dimensional projections in $p$-dimensional space. Let $X_{n \times p}$ be the original data whose projections are of our interest. A projection basis, $A_{p \times d}$, characterises the direction from which the high-dimensional data are projected. A constraint that projection bases needs to satisfy is the orthonormality condition (which requires each axis to be unit vector and perpendicular to each other). This gives the basis space a geometrical structure of a Stiefel manifold. The projection of the original data on a basis hence can be defined as $Y = X \cdot A$. The projection is usually in 1D or 2D for the purpose of visual display.
